Turbulence in compact to giant HII regions

### 2022-09-20 strucfunc_paper.tex
Finish unfinished sentence

Figure~\ref{fig:rvsR} shows the relation between the
correlation length \(r_0\) of the velocity fluctuations
and the diameter \(D_{\hii}\) of the \hii{} region. 
The relationship we find is
\(\log r_0 = (0.95 \pm 0.33) \log D_{\hii} - (1.6 \pm 0.7)\),
which is very close to linear,
implying that the correlation length is a fixed fraction
\( r_0 /  \log D_{\hii} = \)
.
The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the determination of their size is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.

>>>>

Figure~\ref{fig:rvsR} shows the relation between the
correlation length \(r_0\) of the velocity fluctuations
and the diameter \(D_{\hii}\) of the \hii{} region. 
The relationship we find is
\(\log r_0 = (0.95 \pm 0.33) \log D_{\hii} - (1.6 \pm 0.7)\),
which is very close to linear,
implying that the correlation length is a fixed fraction
of the diameter:
\( r_0 /  \log D_{\hii} = 0.02 \pm 0.01\).

The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the determination of their size is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.
